\documentclass[11pt]{article}

%-------------------------------
% Package imports and formatting
%-------------------------------
\usepackage{xcolor}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[colorlinks,allcolors=blue!80!black]{hyperref}
\usepackage[normalem]{ulem}
\usepackage[a4paper,%
            left=.5in,right=.5in,top=.5in,bottom=.5in,%
            footskip=.25in]{geometry}
\usepackage{tabto}
\usepackage{fontawesome}
\usepackage{fancyhdr}

%-------------------------------
% Footer settings
%-------------------------------
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\pagestyle{fancy}
\pagenumbering{gobble}
\rfoot{\today}

%-------------------------------
% Title spacing
%-------------------------------
\titlespacing{\section}{0pt}{\parskip}{-\parskip}

%-------------------------------
% Document starts
%-------------------------------
\begin{document}

%-------------------------------
% Name and Contact
%-------------------------------
\noindent
\centerline{\huge \textbf{JOHN W HODSON}}\\[14pt] % Adjusted whitespace here
\vspace{0.2cm}
\faEnvelopeSquare \,\href{mailto:hodsonus@gmail.com}{hodsonus@gmail.com}
\hfill
\faHome \,\href{https://hodsonus.com}{hodsonus.com}
\hfill
\faGithub \,\href{https://github.com/hodsonus}{hodsonus}
\hfill
\faMobilePhone \,(727) 348-2899

%-------------------------------
% PROFESSIONAL SUMMARY
%-------------------------------
\vspace{0.6cm}
\section*{PROFESSIONAL SUMMARY}
\hrule
\vspace{0.3cm}
\noindent
Results-driven Senior Software Engineer at Microsoft with extensive experience designing and deploying large-scale, cloud-based services. Technical lead for projects ranging from cross-tenant collaboration features to comprehensive tenant backup and recovery services in Entra~ID. Skilled in driving initiatives from concept to implementation, coordinating large teams, and collaborating with partner organizations. Passionate about security, performance, and delivering reliable services to billions of enterprise and consumer users.

%-------------------------------
% EXPERIENCE
%-------------------------------
\vspace{0.6cm}
\section*{EXPERIENCE}
\hrule
\vspace{0.3cm}

\noindent
\textbf{Microsoft,} Redmond, WA\\
\emph{Senior Software Engineer}\\
\noindent\textbf{Entra ID Tenant Backup \& Recovery} \hfill\textit{June 2024 -- Present}
\begin{itemize}[noitemsep,nolistsep,label={-}]
	\item Led a team of 7 engineers and 3 product managers to design and prototype a tenant backup/recovery system for restoring large-scale enterprise customer tenants consisting of tens of millions of objects to previous states.
	\item Authored end-to-end design, cost analysis, privacy data flow, and threat model; collaborated with cross-org leadership to finalize approach.
	\item Implemented two orchestrator Kubernetes microservices enabling administrators to start, monitor, and manage asynchronous recovery jobs with robust logging and fault detection.
	\item Mentored junior engineers on code quality, architectural best practices, and on-call readiness. Fostered a collaborative team culture via “Ask Me Anything” and “Recovery Games” sessions.
	\item Coordinated weekly customer feedback sessions and integrated real-world requirements into product design.
\end{itemize}

\noindent\textbf{Entra ID Cross-Tenant Access Settings} \hfill\textit{August 2020 -- June 2024}
\begin{itemize}[noitemsep,nolistsep,label={-}]
	\item Owner of the \href{https://learn.microsoft.com/en-us/entra/external-id/cross-tenant-access-overview}{cross-tenant access settings MSGraph APIs}, a set of OData REST APIs receiving over 66 million requests per day used to securely model B2B collaboration scenarios.
	\item Designed and rolled out the scalable Cross-Tenant Access Policy (XTAP) solution, migrating over 7 million customer tenants at scale with zero customer disruptions.
	\item Drove cross-org execution with partner teams (Substrate, eSTS, MSA) to unblock new features, mitigate security concerns, and enable advanced B2B scenarios.
\end{itemize}

%-------------------------------
% EDUCATION
%-------------------------------
\vspace{0.6cm}
\section*{EDUCATION}
\hrule
\vspace{0.3cm}
\noindent
\textbf{University of Florida,} Gainesville, FL \hfill{GPA: 3.96/4.00}\\
\textit{Bachelor of Science in Computer Engineering}\\
    \href{https://www.ece.ufl.edu/people/student-awards/}
            {Computer E Award} (most prestigious academic award granted by ECE department),
    \href{https://clas.ufl.edu/undergraduate/anderson-scholars/}
            {Anderson Scholar} (top 1\% academically in graduating class),
    \href{https://www.eng.ufl.edu/leadership/students/scholarships/thomas-o-hunter-leadership/}
            {College of Engineering Scholarship for Engineering Leadership},
    CISE Scholarship,
    ECE Scholarship (x2),
    College of Engineering Dean\rq s List (x4),
    \href{https://en.wikipedia.org/wiki/Bright_Futures_Scholarship_Program}{Bright Futures Florida Academic Scholar (100\% tuition coverage)}

%-------------------------------
% TECHNICAL SKILLS
%-------------------------------
\vspace{0.6cm}
\section*{TECHNICAL SKILLS}
\hrule
\vspace{0.3cm}

\begin{itemize}[noitemsep,nolistsep,label={}]
    \item \textbf{Cloud \& Distributed Systems}
          Azure (CosmosDB, Storage, Service Bus, Key Vault, Service Fabric), 
          Redis, Kubernetes, REST APIs, Microservices, Multi-tenant architecture

    \item \textbf{Programming \& Frameworks}
          C\#, Python, Java, C, C++, Bash, OCaml, .NET, 
          Docker, OData, Azure DevOps (CI/CD), Git

    \item \textbf{Security \& Reliability}
          Threat modeling, privacy data flows, GDPR/Schrems II compliance, monitoring,
          live site on-call

    \item \textbf{Architecture \& Leadership}
          End-to-end design, cost analysis, architecture reviews,
          mentoring junior engineers, cross-org collaboration

\end{itemize}

\end{document}