
\documentclass[11pt]{article} %Sets the default text size to 11pt and class to article.
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage[geometry]{ifsym}
\usepackage[hidelinks]{hyperref}
\usepackage{marvosym}
\usepackage{fontawesome}
\usepackage[a4paper,%
left=.5in,right=.5in,top=.45in,bottom=.45in,%
footskip=.25in]{geometry}
\usepackage{tabto}

\titlespacing{\section}{0pt}{\parskip}{-\parskip}
\newcommand\textbox[1]{%
	\parbox{.333\textwidth}{#1}%
}

\pagenumbering{gobble}

\begin{document}
	
	\noindent\centerline{ \huge\textbf{JOHN W HODSON}}\\
	
	\noindent
	\faEnvelopeSquare \space\href{mailto:hodsonus@gmail.com}{hodsonus@gmail.com} \hspace*{\fill}
	\faHome \space \href{https://www.hodsonus.com}{https://www.hodsonus.com} \hspace*{\fill}
	\faGithub \space \href{https://github.com/hodsonus}{hodsonus} \hspace*{\fill}
	\faMobilePhone \space (727) 348-2899\\
	
	\section*{EDUCATION}
		\hrule \relax
		\vspace{.4cm}
		
		\noindent \textbf{University of Florida,} Gainesville, FL
		\hfill\textbf{GPA: 3.96/4.0}
		\hfill\textbf{August 2016 to May 2020}\\
		\textit{Bachelor of Science in Computer Engineering}
		\begin{itemize}[noitemsep,nolistsep, label = {-}]
			\item  Coursework - 
											Algorithm Design,
											Programming Language Concepts,
											Object Oriented Programming,
											Data Structures \& Algorithms,
											Principles of Computer System Design,
											Operating Systems,
											Computer Networks,
											Database Systems,
											Microprocessor Applications I \& II
			\item  Honors - 
											President's Honor Roll (Spring 2019, Fall 2019),
											College of Engineering Dean\rq s List (Spring 2018, Spring 2019, Fall 2019),
											\href{https://www.sfa.ufl.edu/types-of-aid/bright-futures/}{Bright Futures Florida Academic Scholar (100\% tuition coverage)},
											\href{https://sites.clas.ufl.edu/clas-main/undergraduate/anderson-scholars/anderson-scholars-listing/}{Anderson Scholar (top 1\% academically, class of 2020)}
		\end{itemize}
		
		\vspace{.20cm}
		
	\section*{STUDENT ORGANIZATIONS}
	\hrule \relax
	\vspace{.4cm}
		
		\noindent \href{https://uf-ace.com/}{\textbf{Association of Computer Engineers (ACE),}} Gainesville, FL \hfill\textbf{January 2018 to January 2019}\\
		\textit{External Outreach Chair}
		\begin{itemize}[noitemsep,nolistsep, label={-}]
			\item Planned and implemented biweekly outreach events for a club with a reach of nearly 1000 members.
			\item One of 11 leaders responsible for the management and growth of the organization via discussion and decision making on key issues.
			\item Mentor in the career development mentorship program to underclassmen members.
		\end{itemize}
		\vspace{.20cm}
		
		\noindent \textbf{Sigma Nu Fraternity,} Gainesville, FL \hfill\textbf{January 2019 to January 2020}\\
		\textit{Vice President of Administrative Affairs}
		\begin{itemize}[noitemsep,nolistsep, label={-}]
			\item One of 4 leaders directly responsible for the management of a member body of over 60 individuals.
			\item Maintained records and detailed minutes of many dozen meetings over two semesters.
			\item Assisted in the planning of several philanthropic events, including the annual $\Sigma$N Sets and Nets, benefiting St. Jude Children's Research Hospital.
		\end{itemize}
		\vspace{.20cm}
	
	\section*{COLLEGE \& DEPARTMENT LEADERSHIP}
	\hrule \relax
	\vspace{.4cm}
	
	\noindent\textbf{\href{https://www.eng.ufl.edu/leadership/students/scholarships/thomas-o-hunter-leadership/}{Thomas O. Hunter Leadership Scholarship}} \hfill\textbf{2019 - 2020}
	\begin{itemize}[noitemsep,nolistsep, label={-}]
		\item Awarded by the Herbert Wertheim College of Engineering at the University of Florida.
		\item Leadership Scholarship Award intended to identify 6 future leaders in the field of engineering and highlight and award those who have displayed exceptional merit in leadership activities and academic scholarship.
	\end{itemize}
	\vspace{.20cm}
	
	\noindent\textbf{Helen E. Khouri Memorial Scholarship} \hfill\textbf{2019 - 2020}
	\begin{itemize}[noitemsep,nolistsep, label={-}]
		\item Awarded by the Department of Electrical and Computer Engineering (ECE) at the University of Florida for excellence in academics, extracurriculars, and leadership in student organizations.
	\end{itemize}
	\vspace{.20cm}
	
	\noindent\textbf{Matthew Martin Memolo Memorial Scholarship} \hfill\textbf{2018 - 2019}
	\begin{itemize}[noitemsep,nolistsep, label={-}]
		\item Awarded by the Department of Computer and Information Science and Engineering (CISE) at the University of Florida to 10 ``outstanding'' CISE undergraduates in a department of over 2,500 students.
	\end{itemize}
	\vspace{.20cm}

	\noindent\textbf{Ralph Sias Scholarship} \hfill\textbf{2018 - 2019}
	\begin{itemize}[noitemsep,nolistsep, label={-}]
		\item Awarded by the Department of Electrical and Computer Engineering (ECE) at the University of Florida for excellence in academics, extracurriculars, and leadership in student organizations.
	\end{itemize}
	\pagebreak
	
	\section*{COMMUNITY SERVICE}
	\hrule \relax
	\vspace{.4cm}

	\noindent \href{https://sites.google.com/view/ignitecs/home}{\textbf{Google igniteCS,}} Gainesville, FL \hfill\textbf{January 2017 to May 2018}\\
	\textit{Program Lead (formerly Logistics Director)}
	\begin{itemize}[noitemsep,nolistsep, label = {-}]
		\item Met with Google to discuss and make key decisions on critical aspects of the sponsored program, including curriculum development and volunteer recruitment.
		\item Managed scheduling between Oak View Middle School and our Google igniteCS team of over 30 mentors.
		\item Aided students in a class size of 20 working with VEX iQ Robotics, providing guidance in basic programming principles and hardware implementation as a mentor.
	\end{itemize} 
	\vspace{.20cm}
	
	\section*{PROFESSIONAL EXPERIENCE}
		\hrule \relax
		\vspace{.4cm}
		
		\noindent \textbf{Microsoft,} Redmond, WA \hfill\textbf{May 2019 to August 2019}\\
		\textit{Software Engineer Intern}
		\begin{itemize}[noitemsep,nolistsep, label = {-}]
			\item Developed in the C\# and .NET environment on \href{https://docs.microsoft.com/en-us/azure/active-directory/fundamentals/active-directory-whatis}{Azure's Active Directory}, a cloud-based service responsible for managing user identities, access management, and devices.
			\item Solved a major customer complaint regarding the loss of private BitLocker key data by refactoring API calls and architecting an additional external storage model to decouple the lifetime of two data objects.
			\item Changed the intrinsic way that the Microsoft Mezzo storage service operates by altering their data synchronization service to sync data objects with a one-to-many instead of a one-to-one relationship.
		\end{itemize}
	
		\vspace{.20cm}
		
		\noindent \textbf{Ultimate Software,} Weston, FL \hfill\textbf{May 2018 to August 2018}\\
		\textit{Software Engineer - TechStar Intern}
		\begin{itemize}[noitemsep,nolistsep, label = {-}]
			\item Developed and tested in C\# within the ASP.NET framework in a Kanban-Agile environment on \href{https://www.ultimatesoftware.com/UltiPro-Solution-Features-Payment-Services}{UTE (UltiPro Tax Engine)}, responsible for the collection of over 13,000 tax codes.
			\item Managed and manipulated UTE's T-SQL database with the use of Microsoft SQL Server.
			\item Implemented Grafana dashboard to diagnose performance issues with generation and calculation of tax forms in order to better meet SLAs.
		\end{itemize}
		\vspace{.20cm}
		
\end{document}