\section*{EXPERIENCE}
		\hrule \relax
		\vspace{.4cm}
		
		\noindent \textbf{Microsoft,} Redmond, WA \hfill\textbf{May 2019 to August 2019}\\
		\textit{Software Engineer Intern}
		\begin{itemize}[noitemsep,nolistsep, label = {-}]
			\item Developed in the C\# and .NET environment on \href{https://docs.microsoft.com/en-us/azure/active-directory/fundamentals/active-directory-whatis}{Azure's Active Directory}, a cloud-based service responsible for managing user identities, access management, and devices.
			\item Solved a major customer complaint regarding the loss of private BitLocker key data by refactoring API calls and architecting an additional external storage model to decouple the lifetime of two data objects.
			\item Changed the intrinsic way that the Microsoft Mezzo storage service operates by altering their data synchronization service to sync data objects with a one-to-many instead of a one-to-one relationship.
		\end{itemize}
	
		\vspace{.20cm}
		
		\noindent \textbf{Ultimate Software,} Weston, FL \hfill\textbf{May 2018 to August 2018}\\
		\textit{Software Engineer - TechStar Intern}
		\begin{itemize}[noitemsep,nolistsep, label = {-}]
			\item Developed and tested in C\# within the ASP.NET framework in a Kanban-Agile environment on \href{https://www.ultimatesoftware.com/UltiPro-Solution-Features-Payment-Services}{UTE (UltiPro Tax Engine)}, responsible for the collection of over 13,000 tax codes.
			\item Managed and manipulated UTE's T-SQL database with the use of Microsoft SQL Server.
			\item Implemented Grafana dashboard to diagnose performance issues with generation and calculation of tax forms in order to better meet SLAs.
		\end{itemize}
		\vspace{.20cm}
		
		\noindent \href{https://sites.google.com/view/ignitecs/home}{\textbf{Google igniteCS,}} Gainesville, FL \hfill\textbf{January 2017 to May 2018}\\
		\textit{Program Lead (formerly Logistics Director)}
		\begin{itemize}[noitemsep,nolistsep, label = {-}]
			\item Communicated directly with Google and make key decisions on critical aspects of the program.
			\item Managed scheduling between Oak View Middle School and our Google igniteCS team of over 30 mentors.
			\item Aided students in a class of $\sim$20 working with VEX iQ Robotics, providing guidance in basic programming principles and hardware implementation as a mentor.
		\end{itemize} 
		\vspace{.20cm}
		
		\noindent \href{https://uf-ace.com/}{\textbf{Association of Computer Engineers (ACE),}} Gainesville, FL \hfill\textbf{January 2018 to January 2019}\\
		\textit{External Outreach Chair}
		\begin{itemize}[noitemsep,nolistsep, label={-}]
			\item Planned and implemented biweekly outreach events for a club with a reach of nearly 1000 members.
			\item One of 11 leaders responsible for the management/growth of ACE via decision making on key issues.
			\item Participant in career development mentorship pairing program as an active member.
		\end{itemize}
		\vspace{.20cm}